canaper: Categorical analysis of neo- and paleo-endemism in R

### 2022-10-05 ms/ms.Qmd
Update targets plan
get mac hardware info outside of docker

# Load CANAPE results from canaper and biodiverse
tar_load(c(
  acacia_canape_biod,
  acacia_canape_comp,
  acacia_biod_elapsed_min,
  acacia_canape_cpr_1,
  acacia_canape_cpr_2,
  acacia_canape_cpr_3),
  store = here::here("_targets")
)

>>>>

# Load CANAPE results from canaper and biodiverse
tar_load(c(
  acacia_canape_biod,
  acacia_canape_comp,
  acacia_biod_elapsed_min,
  acacia_canape_cpr_1,
  acacia_canape_cpr_2),
  store = here::here("_targets")
)
